Survey.jl - An Efficient Framework for Analysing Complex Surveys

### 2024-09-15 paper/header.tex
Year is 2023

\hypersetup{
pdftitle = {Survey.jl - An Efficient Framework for Analysing Complex Surveys},
pdfsubject = {JuliaCon 2024 Proceedings},
pdfauthor = {Ayush Patnaik, Nadia Enhaili, Siddhant Chaudhary, Shikhar Mishra, Iulia Dumitru},
pdfkeywords = {Julia, Survey, Statistics, Sampling},
}

>>>>

\hypersetup{
pdftitle = {Survey.jl - An Efficient Framework for Analysing Complex Surveys},
pdfsubject = {JuliaCon 2023 Proceedings},
pdfauthor = {Ayush Patnaik, Nadia Enhaili, Siddhant Chaudhary, Shikhar Mishra, Iulia Dumitru},
pdfkeywords = {Julia, Survey, Statistics, Sampling},
}
